---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cryptoapi

<!-- badges: start -->
<!-- badges: end -->

The goal of cryptoapi is to be a wrapper that imports and analyzes data from Binance, Binance US, Bitstamp, Bittrex, Coinbase, Coinbase Pro, Crypto.com, FTX, FTX US, Gemini, Huobi, Kraken, Kucoin, and Poloniex. 

Use at your own risk.

## Installation

You can install the development version of cryptoapi from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cstjohn810/cryptoapi")
```

## Example

This is a basic example:

```{r example}
library(cryptoapi)
library(magrittr)
```

Can pull out the current ticker price of any asset from any exchange:

```{r}
public_ticker_price(exchange = "binance", base_asset = "BTC", quote_asset = "USD")
```

Alternatively, get extra price information by toggling the price_only option:

```{r}
public_ticker_price(exchange = "ftx", base_asset = "BTC", quote_asset = "USD", price_only = FALSE)
```

If necessary, find the available assets for any exchange:

```{r}
public_asset_list(exchange = "crypto.com")
```

View order book for varying depths:

```{r}
public_order_book(exchange = "coinbase-pro", level = 2)
```

View candle information (OHLC):

```{r}
public_candles("gemini", time_frame = "1m") %>% 
  head(1)
```

View recent trades:

```{r}
public_trades(exchange = "kraken")
```
View additional asset information:

```{r}
public_asset_info("gemini")
```

